A multi-scalar model for system of cities

### 2019-10-01 Docs/Communications/2019/CCS2019/Communication/slides.tex
calib_results

$\rightarrow$ model implemented in \texttt{scala} and integrated within a broader library (including implementations of \cite{raimbault2018indirect} \cite{raimbault2018calibration} \cite{favaro2011gibrat} \cite{cottineau2015modular})

@@

\begin{center}
\includegraphics[width=0.55\textwidth]{figures/openmole.png}
\end{center}

(X year of computation for the results presented here)

@@

\textit{For all indicators, median sharpe ratios computing for a parameter point across repetitions are all larger than 1.6}
%(min around 1 for 3 indicators, above 5 for 2 and around 0.5 for 2)}

@@

\includegraphics[width=0.8\textwidth]{figures/allindics_hist.png}

@@

\begin{center}
\includegraphics[height=0.8\textheight]{figures/deltaHierarchymacroPopulations-mesoTimeSteps_colorMacroInteractionDecay_facetmesoMacroDecayUpdateMax-macroMesoBetaUpdateMax.png}
\end{center}

\footnotesize
\textit{Non-trivial influence of coupled feedbacks on the different scales}

@@

% TODO 
%\sframe{Calibration}{
%}

>>>>

$\rightarrow$ model implemented in \texttt{scala} and integrated within a broader library (including implementations of \cite{raimbault2018indirect} \cite{raimbault2018calibration}

\cite{favaro2011gibrat} \cite{cottineau2015modular})

@@

\begin{center}
\includegraphics[height=0.13\textheight]{figures/iconOM.png}
\includegraphics[height=0.13\textheight]{figures/openmole.png}
\end{center}

%(X year of computation for the results presented here)

\footnotesize
\textit{Enables seamlessly (i) model embedding; (ii) access to HPC resources; (iii) exploration and optimization algorithms}

\textbf{Come to the satellite \textit{New Methods and Epistemologies to Explore Simulation Models} tomorrow afternoon in LHN-TR+05}

@@

%(min around 1 for 3 indicators, above 5 for 2 and around 0.5 for 2)}

@@

\begin{center}
\includegraphics[width=0.8\textwidth]{figures/allindics_hist.png}
\end{center}

\textit{For all indicators, median sharpe ratios computing for a parameter point across repetitions are all larger than 1.6}

@@

\begin{center}
\includegraphics[height=0.75\textheight]{figures/deltaHierarchymacroPopulations-mesoTimeSteps_colorMacroInteractionDecay_facetmesoMacroDecayUpdateMax-macroMesoBetaUpdateMax.png}
\end{center}

%\footnotesize
\textit{Non-trivial influence of coupled feedbacks on the different scales}

@@

\sframe{Multiscale optimization}{

\begin{center}
	\includegraphics[width=0.8\textheight]{figures/pareto_macroHierarchy-mesoHierarchy.png}
\end{center}

\textit{Pareto front obtained with Genetic Algorithm optimization for two contradictory objective of macrosopic and mesoscopic hierarchies}
